Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-11-27 paper/paper.tex
changed title
Added some refs

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title Is Hope}

@@

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

@@

The task of differentially private synthetic data is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data}

@@

% \received{20 February 2007}
% \received[revised]{12 March 2009}
% \received[accepted]{5 June 2009}

@@

The task of differentially private synthetic data\cite{NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
